Followers Are Not Enough: A Multi-faceted Approach to Community Detection in Online Social Networks

### 2014-11-20 paper-postreview/results.tex
modif sec 3.4

On an individual-based level, we also found some interesting cases of membership to different communities, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to. 
For example, the user @JohnReaves belongs to two different topic communities: one talking about healthcare and the other talking about innovation and creativity. There is a almost $70\%$ overlap between the users in the innovation and creativity topic community and the interaction-based community and the activity-based community the user is in, whereas there is almost no overlap between these two and the healthcare community. This means that he interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
Secondly, user @jenajean also belongs to two different topic communities: she talks about Nasa and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic communitiy). The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does NOT overlap with the topic community a part for one or two users max. Therefore they interact with other groups of people.

>>>>

On an individual-based level, we also found some interesting cases of membership to different communities, which show that asking different questions leads indeed to finding different kinds of communities a user belongs to. 
For example, the user @JohnReaves belongs to two different topic communities: one talking about healthcare and the other talking about innovation and creativity. There is a almost $70\%$ overlap between the users in the innovation and creativity topic community and the interaction-based community and the activity-based community the user is in, whereas there is almost no overlap between these two and the healthcare community. This means that he interacts and behaves alike the people talking about innovation and creativity, whereas he also talks about healthcare but he does not interact with (nor behave alike) the people talking about that.
Secondly, user @jenajean also belongs to two different topic communities: she talks about Nasa and space but she does not interact nor behave alike people in that communities, whereas she also talks a lot about leadership, and the people she interacts with highly overlap with the people belonging to the topic-based community on leadership she belongs to.
Lastly, @rajean, @Tekee, @Kimbirly and @mamamonroe are examples of users belonging to the topic community talking about Denver and Colorado (and to only that topic communitiy). The activity-based community they belong to highly overlaps with the topic community (therefore they behave like the people that talk about Colorado), but they belong to different interaction-based communities, each of which does not overlap with the topic community a part for one or two users. Therefore they interact with other groups of people.
